Forecasting the old-age dependency ratio to determine a sustainable pension age

### 2021-05-05 PensionAge_anzjs.tex
Satisfying ANZJS style rules

\usepackage{float, bm}
\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage{lineno}
\usepackage[UKenglish]{isodate}
\usepackage{hyperref}

@@

\usepackage{titling}
\pretitle{\begin{center}\Large\bfseries}
\posttitle{\end{center}\vspace{0.5cm}}
\preauthor{\begin{center}\large}
\postauthor{\end{center}\begin{center}
$^1$\emph{Department of Econometrics \& Business Statistics, Monash University, Clayton, Australia}\\
$^2$\emph{Shanghai, China}\\
$^3$\emph{Macquarie University, Sydney, Australia}
\footnotetext{$^*$Corresponding author. Email: \texttt{Rob.Hyndman@monash.edu}}\end{center}}

@@

We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population. Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries.

@@

Australia's ageing population is a result of three factors: (1) significant technological advances in medical care leading to longer life spans; (2) high fertility rates after World War II resulting in the ``baby-boomer'' generation; and (3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}. Consequently, there are many older people leaving the workforce, and fewer workers replacing them. Many other countries face similar demographic challenges. One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \citep{Walker1982}. The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.

@@

The government has not disclosed the method it used to determine the new pension age. \citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that ``pension age should increase by approximately 50\% of any increase in life expectancy''. However, using a ``rule of thumb'' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term. We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates. Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.

@@

We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year t}\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year t}.
\end{align*}

In addition, the net migration\footnote{Net migration is the difference between immigration and emigration in a certain area during a specified time frame.} (denoted \(G\)) is estimated using demographic growth-balance equations, which summarize the relationship between population change and three factors: net migration, births and deaths. The equations are expressed as:
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
\end{align*}
where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to migration in calendar year \(t\) of persons born during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\). The deaths are estimated using the standard life table approach of population projection \citep{Preston2000}. It should be noted that the estimated net migration includes errors in data recording.

@@

Variants of the Lee-Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}. The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee-Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee-Carter method failed to capture. The Hyndman-Ullah method (2007) is a generalization of the Lee-Carter method and is used as the basis for forecasting demographic components in this study. In addition, the product-ratio method \citep{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.

\hypertarget{lee-carter-method}{%
\subsubsection*{Lee-Carter method}\label{lee-carter-method}}
\addcontentsline{toc}{subsubsection}{Lee-Carter method}

The Lee-Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
\begin{equation}\label{eq:lc}
  \log m_{t}(x)=\mu(x)+\phi(x)\beta_{t}+\varepsilon_{t,x},
\end{equation}
where \(m_{t}(x)\) is the central death rate for age \(x\) in year \(t\). This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(\mu(x)\)\} and \{\(\phi(x)\)\}, and a time-varying index \(\beta_{t}\). \(\phi(x)\) is a set of parameters that tell us the rate at which each age responds to changes in \(\beta_{t}\). \(\beta_{t}\) measures the general level of the log death rates; \(\mu(x)\) is the general pattern across the age of the log mortality rate and \(\varepsilon_{t,x}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

@@

\hypertarget{hyndman-ullah-method}{%
\subsubsection*{\texorpdfstring{Hyndman-Ullah method \label{sec:HU}}{Hyndman-Ullah method }}\label{hyndman-ullah-method}}
\addcontentsline{toc}{subsubsection}{Hyndman-Ullah method \label{sec:HU}}

@@

The Hyndman-Ullah (HU) model can be written as
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1}\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
\end{align}
where \(y_t(x)\) may be log mortality, log fertility or net migration \citep{HB08} in year \(t\) and age \(x\). Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalized regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score. The \(e_t(x)\) is the model error having mean zero and no serial correlation, while \(\mu(x)\) is estimated as the average of \(s_t(x)\) across years. Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j^{th}\) principal components and scores of \(s_t(x)-\mu(x)\) respectively. Following \citet{HB08}, we select \(J=6\) which we have found to be large enough for demographic applications.

By conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of \(y_{T+h}(x)\) are given by
\begin{equation}
  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
\end{equation}
where \(\widehat{\beta}_{T+h\mid T,j}\) denotes the \(h\)-step-ahead forecast of \(\beta_{T+h\mid T,j}\). Because \(\left\{\beta_{t,j}\right\}\) is time-varying, it controls the dynamics of the process. Each component series \(\left\{\beta_{t,j}\right\}\) is modelled with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are selected using the automated algorithm of \citet{forecastpackage}, and the parameters are estimated using maximum likelihood estimation.

@@

When we apply the \citet{HU07} model to data on males and females, we need to constrain the resulting forecasts so they do not diverge. In the product-ratio method \citep{HBY13}, the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently. That is, define
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, the HU method is applied to these two new variables:
\begin{align*}
  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x)\\
  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x)
\end{align*}
where time series \(\left\{\beta_{t,j}\right\}\) are fitted with ARIMA models while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to \(0<d<\frac{1}{2}\)). It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecasts of male and female do not diverge. Then, forecasts of sex-specific data are obtained using
\begin{align*}
  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x)\\
  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x)
\end{align*}
The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.

@@

Following the general procedure proposed in \citet{HB08}, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future. We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration. We used weighted penalized splines \citep{HU07} when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births. We use loess when estimating the net-migration curves.

@@

There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman-Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.

@@

The first basis function \(\widehat{\phi}_1(x)\) measures the different effects of the time-trend across ages. It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception. The two ``bumps'' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s. The second basis function, accounting for 31.5\% of the variation, largely concerns mothers aged over 30. The forecasts of future coefficients are shown as the blue lines in the lower panels with their 80\% pointwise prediction intervals shown as blue shaded regions. These forecasts are obtained using automatically selected ARIMA models. In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts, only account for 4.6\% of the variation, and are much harder to interpret.

Similar models are used for the product and ratio of mortality rates, and sum and different of net migration rates.

@@

Figure \ref{fig:totalpopulationbyyears} shows the forecast of the total population by sex over the prediction horizon, while Figure \ref{fig:totalpopulationin2038} shows the 20-year forecast of population age structure in 2038. Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to around 27 million by 2068.

@@

Historical OADR values are shown in black in Figure \ref{fig:OADRcurrent} for 1921--2019. The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \citep{IGR02} and 2007 \citep{IGR07}. The increased trend from 2010 is due to the retirements of ``Baby Boomers'', born after WW2. We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRcurrent-1.pdf}
\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65 (green), the current approved pension age scheme (orange), and the proposed scheme with the pension age rising to 70 in 2035 (purple). The actual OADRs for 1921--2019 are shown in black.}
\end{figure}

Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal of 65. This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care. Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035. This proposal also leads to a slow decline in the OADR over the next 15 years. Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.

@@

Let \(a_t\) denote the pension age in year \(t\), and we denote a pension age scheme over the prediction horizon by \(\bm{P}=[a_{T+1},\dots,a_{T+H}]'\), with the corresponding OADR values given by \(O_{T+1},\dots,O_{T+H}\). Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold. We impose the constraint \(0 \le a_t - a_{t-1} < 1\) to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension. We also assume that the adjustment unit of the pension age is one month, for easier implementation.

@@

In addition to finding the target pension age based on the mean value of OADR, we also find ``plausible'' pension age schemes that could give the desired OADR level. Specifically, we find a range of pension age schemes for which \(O^*\) is contained within the 80\% prediction intervals of the simulated \(O_{T+H|T}\) values. Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80\% prediction intervals of OADR is equal to the desired OADR level. Hence, any pension age scheme within those two boundaries is plausible. The range of plausible pension age schemes can be thought of as an 80\% confidence interval of pension age schemes where we are 80\% sure that they will give the desired outcome.

@@

Figure \ref{fig:comparisonofpensionages} shows (in blue) the pension scheme produced by this algorithm, along with 80\% confidence intervals. In comparison, the previous (green), current (red) and proposed (orange) schemes are also shown.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/comparisonofpensionages-1.pdf}
\caption{\label{fig:comparisonofpensionages}The target pension age scheme (in blue) along with the pension age schemes that have been set and proposed by the government. The blue shaded region shows 80\% confidence intervals for the target pension age.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRwithoptimal-1.pdf}
\caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme shown in blue, along with the desired OADR level in gray.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRboundaries-1.pdf}
\caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR (in blue) associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level in gray.}
\end{figure}

@@

The data and code to fully reproduce our results is available at \href{https://github.com/robjhyndman/PensionAge}{\texttt{https://github.com/robjhyndman/PensionAge}}. We used R \citep{RCore}, along with the drake \citep{Rdrake}, tidyverse \citep{Rtidyverse}, demography \citep{Rdemography} and forecast \citep{Rforecast} packages.

>>>>

\usepackage{float, bm}
\usepackage{moreverb}
\usepackage{url}
\usepackage{grffile}
\usepackage{lineno}
\usepackage[UKenglish]{isodate}
\usepackage{hyperref}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}

@@

\usepackage{titling}
\pretitle{\begin{center}\Large\bfseries}
\posttitle{\end{center}\vspace{0.5cm}}
\preauthor{\begin{center}\large}
\postauthor{\end{center}\begin{center}
$^1$\emph{Department of Econometrics \& Business Statistics, Monash University, Clayton, Australia}\\
$^2$\emph{Shanghai, China}\\
$^3$\emph{Macquarie University, Sydney, Australia}
\footnotetext{$^*$Corresponding author. Email: \texttt{Rob.Hyndman@monash.edu}. This work is supported by the ARC Centre of Excellence for Mathematical and Statistical Frontiers.}\end{center}}

@@

We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population. Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23\%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-age dependency ratio and to other countries.

@@

Australia's ageing population is a result of three factors: 1) significant technological advances in medical care leading to longer life spans; 2) high fertility rates after World War II resulting in the `baby-boomer' generation; and 3) a large decline in fertility rates over the past thirty years \citep{Fehr2008}. Consequently, there are many older people leaving the workforce, and fewer workers replacing them. Many other countries face similar demographic challenges. One way of measuring this problem is via the old-age dependency ratio (OADR): the number of people post-retirement to the number of people of working age \citep{Walker1982}. The OADR has been increasing for many decades, but recently the rate of increase has jumped markedly, and we show that it will continue to increase at a rapid rate if there are no age-related policy changes.

@@

The government has not disclosed the method it used to determine the new pension age. \citet[p7]{CEDA07} proposed directly linking pension age with life expectancy in the way that `pension age should increase by approximately 50\% of any increase in life expectancy'. However, using a `rule of thumb' approach might not be ideal, as 50\% of the change in life expectancy may not be a good adjustment to pension age in the long term. We propose that the pension age should be linked to the old age dependency ratio, and based on forecasts of future mortality and fertility rates. Our approach has the advantage that it can be used to justify the change in pension age and directly links the pension age with the goal of a stable financial burden for the public.

@@

We can obtain historical mortality rates \(m_t(x)\) (also called central death rates) and fertility rates \(f_t(x)\) as follows:
\begin{align*}
  m_t(x) & = \frac{D_t(x)}{E_t(x)}=\text{age-sex-specific central death rates in calendar year $t$};\\
  f_t(x) & = \frac{B_t(x)}{E^F_t(x)}=\text{age-specific fertility rates in calendar year $t$}.
\end{align*}

The net migration is the difference between immigration and emigration in a certain area during a specified time frame. We denote net migration by \(G\), and estimate it using demographic growth-balance equations, which summarise the relationship between population change and three factors: net migration, births and deaths. The equations are expressed as:
\begin{align*}
  G_t(x,x+1)     & =P_{t+1}(x+1)-P_t(x)+D_t(x,x+1)\qquad\text{for $x=0,1,2,\dots,p-2$},\\
  G_t(p-1^+,p^+) & =P_{t+1}(p^+)-P_t(p^+)-P_t(p-1)+D_t(p-1^+,p^+),\\
  G_t(B,0)       & =P_{t+1}(0)-B_t+D_t(B,0),
\end{align*}
where \(G_t(x,x+1)\) refers to net migration in calendar year \(t\) of persons aged \(x\) at the beginning of year \(t\), \(G_t(p-1^+,p^+)\) refers to migration in calendar year \(t\) of persons aged \(p-1\) and older at the beginning of year \(t\), and \(G_t(B,0)\) refers to migration in calendar year \(t\) of persons born during year \(t\); and similarly for deaths, \(D_t(x,x+1)\), \(D_t(p-1^+,p^+)\), and \(D_t(B,0)\). The deaths are estimated using the standard life table approach of population projection \citep{Preston2000}. It should be noted that the estimated net migration includes errors in data recording.

@@

Variants of the Lee--Carter method \citep{LC92} are frequently used for demographic forecasting \citep[see, e.g.,][]{SBH11}. The most recent forecast of the population in Australia by the \citet{PC13} was based on basic Lee--Carter methods plus some judgement-based adaptations to address the characteristics of demographic trends that the Lee--Carter method failed to capture. The Hyndman--Ullah method (2007) is a generalisation of the Lee--Carter method and is used as the basis for forecasting demographic components in this study. In addition, the product-ratio method \citep{HBY13} is used to eliminate the potential long-term divergence between female and male mortality rates and net-migration rates.

\hypertarget{leecarter-method}{%
\subsubsection*{Lee--Carter method}\label{leecarter-method}}
\addcontentsline{toc}{subsubsection}{Lee--Carter method}

The Lee--Carter (LC) method has been widely used to forecast mortality rates across various countries, including Australia. The model proposed by \citet{LC92} (but using our notation) is
\begin{equation}\label{eq:lc}
  \log m_{t}(x)=\mu(x)+\phi(x)\beta_{t}+\varepsilon_{t,x},
\end{equation}
where \(m_{t}(x)\) is the central death rate for age \(x\) in year \(t\). This model involves fitting a matrix of log central death rates with sets of age-specific constants, \{\(\mu(x)\)\} and \{\(\phi(x)\)\}, and a time-varying index \(\beta_{t}\). The notation \(\phi(x)\) denotes a set of parameters that tell us the rate at which each age responds to changes in \(\beta_{t}\). \(\beta_{t}\) measures the general level of the log death rates; \(\mu(x)\) is the general pattern across the age of the log mortality rate and \(\varepsilon_{t,x}\) is an error term with zero mean and constant variance, reflecting the randomness that can't be captured by the model.

@@

\hypertarget{hyndmanullah-method}{%
\subsubsection*{\texorpdfstring{Hyndman--Ullah method \label{sec:HU}}{Hyndman--Ullah method }}\label{hyndmanullah-method}}
\addcontentsline{toc}{subsubsection}{Hyndman--Ullah method \label{sec:HU}}

@@

The Hyndman--Ullah (HU) model can be written as
\begin{align}
  y_t(x) & = s_t(x) + \sigma_t(x)\varepsilon_{t,x}\label{eq:HU_1},\\
  s_t(x) & = \mu(x) + \sum_{j=1}^{J}\beta_{t,j}\phi_j(x) + e_t(x)\label{eq:HU_2},
\end{align}
where \(y_t(x)\) may be log mortality, log fertility or net migration \citep{HB08} in year \(t\) and age \(x\). Here \(s_t(x)\) is a smoothed version of the observed data \(y_t(x)\), smoothed over age but not time, and estimated by constrained weighted penalised regression splines; and \(\{\varepsilon_{t,x}\}\) are independent and identically distributed standard normal error terms. Equation \eqref{eq:HU_2} has a similar structure to the LC method, except that it is applied to smoothed data and incorporates more than one principal component and score. The \(e_t(x)\) is the model error having mean zero and no serial correlation, while \(\mu(x)\) is estimated as the average of \(s_t(x)\) across years. Estimates of \(\phi_j(x)\) and \(\beta_{t,j}\) are the \(j\)th principal components and scores of \(s_t(x)-\mu(x)\) respectively. Following \citet{HB08}, we select \(J=6\), which we have found to be large enough for demographic applications.

By conditioning on the observed data \(\bm{I}=\left\{{y_1(x),\dots,y_n(x)}\right\}\) and the set of functional principal components \(\bm{B}=\left\{{\phi_1(x),\phi_2(x),\dots,\phi_j(x)}\right\}\), the \(h\)-step-ahead forecast of \(y_{T+h}(x)\) is given by
\begin{equation}
  \widehat{y}_{T+h\mid T}(x)=\widehat{s}_{T+h\mid T}(x) = \text{E}[\widehat{s}_{T+h\mid T}(x)\mid \bm{I, B}] = \widehat{\mu}(x)+\sum_{j=1}^{J}\phi_j(x)\widehat{\beta}_{T+h\mid T,j},
\end{equation}
where \(\widehat{\beta}_{T+h\mid T,j}\) denotes the \(h\)-step-ahead forecast of \(\beta_{T+h\mid T,j}\). Because \(\left\{\beta_{t,j}\right\}\) is time-varying, it controls the dynamics of the process. Each component series \(\left\{\beta_{t,j}\right\}\) is modelled with an ARIMA\((p_j,d_j,q_j)\) process, where \(p_j,d_j,q_j\) are selected using the automated algorithm of \citet{forecastpackage}, and the parameters are estimated using maximum likelihood estimation.

@@

When we apply the \citet{HU07} model to data on males and females, we need to constrain the resulting forecasts so they do not diverge. In the product-ratio method \citep{HBY13}, the HU model is applied to the geometric mean of male and female log mortality data, and the ratio of male and female log mortality data, rather than to each series independently. That is, define
\begin{align}
  p_t(x)&=\sqrt{s_{t}^{\text{M}}(x)s_{t}^{\text{F}}(x)}, \label{eq:coherent_1}\\
  r_t(x)&=\sqrt{\frac{s_{t}^{\text{M}}(x)}{s_{t}^{\text{F}}(x)}}. \label{eq:coherent_2}
\end{align}
Then, the HU method is applied to these two new variables:
\begin{align*}
  \log[p_t(x)]=\mu_p(x)+\sum_{j=1}^{J}\beta_{t,j}\phi_j(x)+e_t(x),\\
  \log[r_t(x)]=\mu_r(x)+\sum_{l=1}^{L}\gamma_{t,l}\psi_l(x)+z_t(x),
\end{align*}
where time series \(\left\{\beta_{t,j}\right\}\) are fitted with ARIMA models, while \(\left\{\gamma_{t,l}\right\}\) are fitted by stationary ARFIMA models (i.e., the order of differencing is constrained to \(0< d < 1/2\)). It is the stationary constraint on \(\gamma_{t,l}\) that ensures the forecasts of male and female do not diverge. Then, forecasts of sex-specific data are obtained using
\begin{align*}
  m_{T+h\mid T}^{\text{M}}(x) & = p_{T+h\mid T}(x)r_{T+h\mid T}(x),\\
  m_{T+h\mid T}^{\text{F}}(x) & = p_{T+h\mid T}(x)/r_{T+h\mid T}(x).
\end{align*}
The method for forecasting net migration by sex is similar to the above method used on mortality rates except no log scale is applied to net migration, and a sum and difference is used rather than a product and ratio.

@@

Following the general procedure proposed in \citet{HB08}, we model each of the five components of population change: female mortality rates, male mortality rates, female net migration, male net migration and fertility rates, and simulate these five components into the future. We use the HU method applied to log-fertility, and the product-ratio method applied to log-mortality and net-migration. We used weighted penalised splines \citep{HU07} when estimating the log-fertility and log-mortality curves, where the weights account for Poisson variation in deaths and births. We use loess when estimating the net-migration curves.

@@

There are three types of randomness in the simulation: (1) randomness from the second equation in the Hyndman--Ullah specification (i.e., \(e_t(x)\) in \eqref{eq:HU_1}); (2) randomness from the ARIMA model fitted to principal component scores; and (3) randomness from the Poisson distribution for births and deaths, or the bootstrap for migrants.

@@

The first basis function \(\widehat{\phi}_1(x)\) measures the different effects of the time-trend across ages. It indicates the general pattern of fertility has little effect on females of age 15, most likely because such pregnancies are almost always accidental and usually prior to the mother taking contraception. The two `bumps' in the first basic function suggests that the historical trend has a distinct impact on females aged around their 20s and 40s. The second basis function, accounting for 31.5\% of the variation, largely concerns mothers aged over 30. The forecasts of future coefficients are shown in the lower panels with their 80\% pointwise prediction intervals shown as shaded regions. These forecasts are obtained using automatically selected ARIMA models. In practice, we use six basis functions, but the four not shown have a much smaller effect on the resulting fertility forecasts, only account for 4.6\% of the variation, and are much harder to interpret.

Similar models are used for the product and ratio of mortality rates, and sum and difference of net migration rates.

@@

Figure \ref{fig:totalpopulationbyyears} shows the forecast of the total population by sex over the prediction horizon, while Figure \ref{fig:totalpopulationin2038} shows the 20-year forecast of population age structure in 2038. Figure \ref{fig:totalpopulationbyyears} indicates that both the female and male population are expected to increase to almost 20 million by 2050.

@@

Historical OADR values are shown in black in Figure \ref{fig:OADRcurrent} for 1921--2019. The strong positive trend indicates an increasing tax burden on workers, consistent with the prediction of the intergenerational reports in 2002 \citep{IGR02} and 2007 \citep{IGR07}. The increased trend from 2010 is due to the retirements of `Baby Boomers', born after WW2. We also show forecasts for three pension schemes: (1) a fixed pension age of 65; (2) the current scheme with the pension age rising to age 67 in 2023; and (3) the proposed pension policy under which the pension ages continues to rise by 6 months every two years until it reaches 70 in 2035.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRcurrent-1.pdf}
\caption{\label{fig:OADRcurrent}Fifty-year forecasts of the OADR associated with a pension age equal to 65, the current approved pension age scheme, and the proposed scheme with the pension age rising to 70 in 2035. The actual OADRs for 1921--2019 are also shown.}
\end{figure}

Once the pension age reaches 67, the OADR under the current policy grows at nearly the same rate as the OADR of a pension age equal to 65. This is consistent with the idea that there is a persistent positive trend in OADR associated with a constant pension age, due to low fertility rates and better health care. Even the proposal to raise the pension age incrementally to 70 by 2035 leads to a similar increasing trend beyond 2035. This proposal also leads to a slow decline in the OADR over the next 15 years. Figure \ref{fig:OADRcurrent} demonstrates that the pension age scheme requires constant review to ensure a stable OADR over the long term.

@@

Let \(a_t\) denote the pension age in year \(t\), and we denote a pension age scheme over the prediction horizon by \(\bm{P}=[a_{T+1},\dots,a_{T+H}]^\top\), with the corresponding OADR values given by \(O_{T+1},\dots,O_{T+H}\). Our goal is to find the minimum pension age in each year that gives an OADR lower than the desired OADR threshold. We impose the constraint \(0 \le a_t - a_{t-1} < 1\) to prevent two undesirable situations: (a) years where no-one is able to retire; and (b) years where retired people become ineligible for the pension. We also assume that the adjustment unit of the pension age is one month, for easier implementation.

@@

In addition to finding the target pension age based on the mean value of OADR, we also find `plausible' pension age schemes that could give the desired OADR level. Specifically, we find a range of pension age schemes for which \(O^*\) is contained within the 80\% prediction intervals of the simulated \(O_{T+H|T}\) values. Because of the monotonic relationship between pension age and OADR, we need only to find the upper (lower) boundary of plausible pension age schemes, at which the upper (lower) limit of 80\% prediction intervals of OADR is equal to the desired OADR level. Hence, any pension age scheme within those two boundaries is plausible. The range of plausible pension age schemes can be thought of as an 80\% confidence interval of pension age schemes where we are 80\% sure that they will give the desired outcome.

@@

Figure \ref{fig:comparisonofpensionages} shows the pension scheme produced by this algorithm, along with 80\% confidence intervals. In comparison, the previous, current and proposed schemes are also shown.

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/comparisonofpensionages-1.pdf}
\caption{\label{fig:comparisonofpensionages}The target pension age scheme along with the pension age schemes that have been set and proposed by the government. The shaded region shows 80\% confidence intervals for the target pension age.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRwithoptimal-1.pdf}
\caption{\label{fig:OADRwithoptimal}The mean forecast and 80\% prediction intervals for the OADR associated with the target pension age scheme, along with the desired OADR level at 0.23.}
\end{figure}

\begin{figure}
\centering
\includegraphics{PensionAge_anzjs_files/figure-latex/OADRboundaries-1.pdf}
\caption{\label{fig:OADRboundaries}The 80\% prediction intervals of OADR associated with the upper and lower boundary of plausible pension age schemes, along with desired OADR level at 0.23.}
\end{figure}

@@

The data and code to fully reproduce our results is available at \href{https://github.com/robjhyndman/PensionAge}{\texttt{https://github.com/robjhyndman/PensionAge}}. We used \textsf{R} \citep{RCore}, along with the \textsf{drake} \citep{Rdrake}, \textsf{tidyverse} \citep{Rtidyverse}, \textsf{demography} \citep{Rdemography} and \textsf{forecast} \citep{Rforecast} packages.
